A Survey of Current Exoskeletons\\ and Their Control Architectures and Algorithms\\ (Draft 3.2)

### 2015-09-30 survey-atkeson.tex
more updates

\url{http://powerexoskeletons.com/}\\
\url{http://exoskeletonreport.com/}\\
\url{http://robohub.org/tag/exoskeleton/}\\
\url{http://robohub.org/exoskeletons-new-and-older/}\\
\url{http://neurogadget.com/tag/exoskeleton}\\
\url{http://www.engadget.com/tag/exoskeleton/}\\
\url{http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-around-the-world}\\
\url{http://spectrum.ieee.org/biomedical/bionics/the-rise-of-the-body-bots}\\
\url{http://www.extremetech.com/electronics/139633-will-we-ever-have-iron-man-exoskeletons}\\
\url{prezi.com/jygcvfxiesnm/a-brief-introduction-to-biomechanical-exoskeletons/}\\
\url{http://news.discovery.com/tech/robotics/exoskeleton-robots-top-5.htm}\\
\url{http://blog.equipoisinc.com/new-technologies-emerging-aerospace-defense-manufacturing/}\\
\url{http://nextbigfuture.com/2015/03/lower-body-exoskeleton-audi-chairless.html}\\
\url{http://www.army-technology.com/features/featuremilitary-exoskeletons-uncovered-ironman-suits-a-concrete-possibility}\\

@@

\noindent
Appears to be a power assist suit for lifting. Sip and puff internface?
Tokyo University of Science Prof. Hiroshi Kobayash.\\
\url{https://innophys.jp/}\\
video: \url{https://www.youtube.com/watch?v=Sqr1l909WPw}\\
video: \url{https://www.youtube.com/watch?v=mNdJgh0ZcrM}\\
video: \url{https://www.youtube.com/watch?v=NtX81pf-3G4}\\
\url{http://blogs.wsj.com/japanrealtime/2014/11/12/wearable-power-assist-device-goes-on-sale-in-japan/}

@@

\noindent
2 devicesin the walking assist program: 1) Bodyweight Support Assist and
Stride Management Assist (SMA):\\
\url{http://corporate.honda.com/innovation/walk-assist/}\\
\url{http://world.honda.com/Walking-Assist/}\\
\url{http://www.slashgear.com/honda-demo-walking-assist-exoskeleton-for-elderly-disabled-2211295/}\\
\url{http://singularityhub.com/2010/09/13/hondas-exoskeletons-help-you-walk-like-asimo-video/}\\

@@

\noindent
Prof Hong Cheng did his Posdoc in CMU from 2006-2009 in CS.
He is very famous in China for his exoskeleton work.\\
Chinese Video: \url{http://society.kankanews.com/s/2014-12-17/0016103932.shtml}\\
\url{http://uestcrobot.net/~hcheng/}\\
\url{http://www.uestcrobot.net/?q=node/291}\\

>>>>

\url{http://powerexoskeletons.com/}\\
\url{http://exoskeletonreport.com/}\\
\url{http://robohub.org/tag/exoskeleton/}\\
\url{http://robohub.org/exoskeletons-new-and-older/}\\
\url{http://neurogadget.com/tag/exoskeleton}\\
\url{http://www.engadget.com/tag/exoskeleton/}\\
\url{http://spectrum.ieee.org/robotics/medical-robots/exoskeletons-around-the-world}\\
\url{http://spectrum.ieee.org/biomedical/bionics/the-rise-of-the-body-bots}\\
\url{http://www.extremetech.com/electronics/139633-will-we-ever-have-iron-man-exoskeletons}\\
\url{https://prezi.com/jygcvfxiesnm/a-brief-introduction-to-biomechanical-exoskeletons/}\\
\url{http://news.discovery.com/tech/robotics/exoskeleton-robots-top-5.htm}\\
\url{http://blog.equipoisinc.com/new-technologies-emerging-aerospace-defense-manufacturing/}\\
\url{http://nextbigfuture.com/2015/03/lower-body-exoskeleton-audi-chairless.html}\\
\url{http://www.army-technology.com/features/featuremilitary-exoskeletons-uncovered-ironman-suits-a-concrete-possibility}\\

@@

\noindent
Appears to be a power assist suit for lifting. Sip and puff interface?
Tokyo University of Science Prof. Hiroshi Kobayash.\\
\url{https://innophys.jp/}\\
video: \url{https://www.youtube.com/watch?v=Sqr1l909WPw}\\
video: \url{https://www.youtube.com/watch?v=mNdJgh0ZcrM}\\
video: \url{https://www.youtube.com/watch?v=NtX81pf-3G4}\\
\url{http://blogs.wsj.com/japanrealtime/2014/11/12/wearable-power-assist-device-goes-on-sale-in-japan/}

@@

\noindent
2 devices in the walking assist program: 1) Bodyweight Support Assist and
Stride Management Assist (SMA):\\
\url{http://corporate.honda.com/innovation/walk-assist/}\\
\url{http://world.honda.com/Walking-Assist/}\\
\url{http://www.slashgear.com/honda-demo-walking-assist-exoskeleton-for-elderly-disabled-2211295/}\\
\url{http://singularityhub.com/2010/09/13/hondas-exoskeletons-help-you-walk-like-asimo-video/}\\

@@

\noindent
Prof Hong Cheng did his Postdoc in CMU from 2006-2009 in CS.
He is very famous in China for his exoskeleton work.\\
Chinese Video: \url{http://society.kankanews.com/s/2014-12-17/0016103932.shtml}\\
\url{http://uestcrobot.net/~hcheng/}\\
\url{http://www.uestcrobot.net/?q=node/291}\\
